### 2017-04-14 src/stats6.tex
Added "Statistical Process Control" to SS6.

>>>>

    \newpage
    \subsection{Control charts}
        \paragraph{Statistical process control}
        Detect and signal when a production lines item-to-item varibility has increased or the process mean has moved form the target.

    \subsubsection{Control of means}
        The most common method of statistical process control is to take regular samples and plot them on a control chart as shown in the following diagram:\\
        \includegraphics[scale=0.125]{controlchart}

        \begin{center}
        \begin{tabularx}{\textwidth}{l|X}
        Event & Action \\
        \hline
        Sample mean is between warning limits & No action \\
        Sample mean between warning and action limits & Take another sample immediently, if the new sample mean is outside warning limits take action \\
        Sample mean outside action limits & Take action \\
        \end{tabularx}
        \end{center}

        \noindent
        To set the limits of a control chart a large sample (when the process is nominal) is taken, known as a proccess capability study. Then find the standard deviation $\sigma$, the size of the continous samples $n$ and the critical values (normaly 95\% and 99.8\%). With this data the confidence itervals for the warning and action limits can be found.

        \begin{example}
        {
            A company manufactures panels for use in making baths. The panels have a target width of 700mm. When a production is satisfactory the widths are normally distributed with a standard deviation of 2mm. Production is to be controlled by taking a regualar sample of 5 panels.
        }

        \begin{step}{Calculate the warning and action limits for a control chart}
        \begin{align*}
        \text{warning limits} &= 700 \pm 1.96 \times \frac{2}{\sqrt{5}}\\
        &= (698.247, 701.753)\\
        &= (698.2, 701.8)
        \end{align*}
        \begin{align*}
        \text{action limits} &= 700 \pm 3.09 \times \frac{2}{\sqrt{5}}\\
        &= (697.236, 702.764) \\
        &= (697.2, 702.8)
        \end{align*}
        \end{step}

        \begin{step}{What action would you take for the following sample $701.2, 698.2, 704.4, 699.4, 695.5$}
        $\bar{x}$ = 699.7\\
        Mean is within warning limits so no action taken.
        \end{step}

        \begin{step}{What action would you take for the following sample $700.2, 697.5, 695.1, 696.0, 698.9$}
        $\bar{x}$ = 697.5\\
        Mean is between warning limit and action limit so another sample should be taken immediently, it it is outside of the warning limits action should be taken.
        \end{step}

        \begin{step}{What action would you take for the following sample $699.5, 707.1, 704.9, 703.9, 706.4$}
        $\bar{x}$ = 704.4\\
        Mean is outside action limits so take action immediently.
        \end{step}

        \paragraph{Target values} Sometimes the target value is not defined/unattainable, it this case a large samples sample mean could be used. In the case were a warning that a process is doint better than expected (i.e. the strength of a iron casting is stronger than expected) an invistigation should be ran to see how the improvement can be maintained.

    \subsubsection{Control of varibility}
        Within a sample their may be high varibility but a normal looking mean, to detect these events we can use a chart for range or a chart for standard deviation. To get the upper and lower limits for these charts multiply the short-term standard deviation by the appropiate value of D/E on table 12 (Control charts for varibility). Standard deviation charts have a better chance to detect a change in varibility with the same rate of false positives as a range chart, however the range is simpler to calculate.

        \begin{example}
        {
            The same company (as in the previous example) wants to control varibility.
        }

        \begin{step}{Calculate upper and lower warning limits for a standard deviation chart}
        \begin{itemize}
        \item Upper action limit $2.15 \times 2 = 4.30$
        \item Upper warning limit $1.67 \times 2 = 3.34$
        \item Lower warning limit $0.35 \times 2 = 0.70$
        \item Lower action limit $0.15 \times 2 = 0.30$
        \end{itemize}
        \end{step}

        \begin{step}{What action would you take for the following sample $701.2, 698.2, 704.4, 699.4, 695.5$}
        $\sigma = 3.328$\\
        Standard deviation is within warning limits so no action taken.
        \end{step}

        \begin{step}{What action would you take for the following sample $700.2, 697.5, 695.1, 696.0, 698.9$}
        $\sigma = 2.077$\\
        Standard deviation is within warning limits so no action taken.
        \end{step}

        \begin{step}{What action would you take for the following sample $699.5, 707.1, 704.9, 703.9, 706.4$}
        $\sigma = 2.991$\\
        Standard deviation is within warning limits so no action taken.
        \end{step}

    \subsubsection{Estimating short-test standard deviation}
        Sometimes its not possible to collect a large sample to find the target value, instead we can estimate it from the range of several samples. Find the range of all the samples then find the mean range. Multiply this value by the suitable b value from table 12 to find an estimate for the standard deviation. Alternativly the b value can be applied to all the ranges and the mean of those values can be used.

        \begin{example}
        {
            9 samples of size 5 from a production process have ranges of:
            $$
            2.3, 2.9, 1.8, 3.4, 2.0, 3.6, 2.9, 2.1, 1.1
            $$
            Estimate the standard deviation of the process
        }

        \begin{step}{}
            \begin{align*}
            \text{mean range} &= \frac{2.3+2.9+1.8+3.4+2.0+3.6+2.9+2.1+1.1}{9}\\
            &= \frac{16.5}{9}\\
            &= 1.8333\\
            \\
            1.8333 \times 0.4299 &= 0.7881\\
            &= 0.788\\
            \end{align*}
        \end{step}

    \subsubsection{Tolerance limits}
        Many processes have limits which the product \textit{must} conform to. For example drugs imagine a drug with a tollerance of 4.9 to 5.1 (for potency) with a target value of 5.0. Its esimated standard deviation was 0.063 which gives the following upper and lower limits.
        \begin{align*}
        z_1 &= \frac{4.9-5.0}{0.063}\\
        &= -1.587\\
        \\
        z_2 &= \frac{5.1-5.0}{0.063}\\
        &= 1.587
        \end{align*}
        which means $1 - 0.887 = 11.3\%$ of the drugs would be outside the tollerance limits.\\
        \\
        If a process's tollerance width exceeds 6 standard deviations the process can be said to meet the tolernaces consitently, given that the mean is kept on target. The drug had a tollerance width of $\displaystyle\frac{0.51 - 0.49}{0.063} = 3.2$ standard deviations.

        \begin{example}
        {
            A biscuit factory produces cream crackers. Packets are sampled at hourly intervals and the weight, in grams, of the contents measured. The results below are from seven samples each of size 5, taken at a time when production was thought to be satisfactory. The target value is 210g.

            \begin{center}
            \begin{tabular}{c|c|c|c|c|c|c}
            \multicolumn{7}{c}{Sample}\\
            1         & 2         & 3         & 4         & 5         & 6         & 7         \\
            \hline
            $209.0$   & $214.5$   & $204.5$   & $217.5$   & $211.0$   & $224.0$   & $210.0$   \\
            $211.0$   & $210.0$   & $209.0$   & $216.0$   & $198.0$   & $220.0$   & $208.0$   \\
            $213.5$   & $212.0$   & $198.5$   & $217.0$   & $209.5$   & $224.0$   & $210.0$   \\
            $205.0$   & $203.5$   & $203.0$   & $214.0$   & $213.5$   & $218.5$   & $220.0$   \\
            $210.0$   & $214.0$   & $213.5$   & $209.5$   & $213.5$   & $210.0$   & $211.0$   \\
            \end{tabular}
            \end{center}
        }

        \begin{step}{Estimate the standard deviation of the process}
        $$\text{ranges} = 8.5, 11, 15, 8, 15.5, 14, 12$$
        $$\text{mean range} = 12$$
        \begin{align*}
        \sigma &= b \times 12 \\
        &= 0.4299 \times 12 \\
        &= 5.1588 \\
        &= 5.16
        \end{align*}
        \end{step}

        \begin{step}{The tollerance for this process is 200g to 220g, comment on the the ability to meet these tollerances}
        The tollerance width is $\displaystyle\frac{220 - 200}{5.16} = 3.88$ standard deviations wide which is bellow the 6 standard deviations we would expect for a process to meet tollerances consistently.
        \end{step}

    \subsubsection{Control of proportion}
        Control charts may also be used when items are classified as conforming/non-conforming (instead of by weight or height etc). Consider a production line were samples were taken when the production was thought to be satisfactory. With a sample size of 100, the following are the number of non-conforming items in each sample:
        $$
        10, 13, 12, 19, 8, 14, 17, 16, 10, 18, 9, 16
        $$
        The total number of non-conforming items are 162, so the estimate for the proportion of non-conforming items would be $\hat{p} = \dfrac{162}{1000} = 0.135$. Given $\hat{p}$ and sample size $n$, we can find the confidence interval for proportion hence we can find the action and warning limits

        \begin{example}
        {
            To control a process producing components for washing machines 75 components are tested every hour and the number of non-conforming components are recorded. The numbers recorded when production was regarded as satisfactory were:
            $$
            6, 16, 12, 9, 14, 19, 7, 13
            $$
        }

        \begin{step}{Find the warning and action limits for a control chart of proportion}
        \begin{align*}
        p &= \frac{6 + 16 + 12 + 9 + 14 + 19 + 7 + 13}{75 * 8}\\
        &= \frac{96}{600}\\
        &= 0.16
        \end{align*}

        \begin{align*}
        \text{action limits} &= 0.16 \pm 3.09 \times \sqrt{\frac{0.16 \times (1 - 0.16)}{75}} \\ 
        &= (0.0292, 0.2908)\\
        \text{warning limits} &= 0.16 \pm 1.96 \times \sqrt{\frac{0.16 \times (1 - 0.16)}{75}} \\
        &= (0.0770, 0.2430)
        \end{align*}
        \end{step}

        \begin{step}{What action would be taken if the next sample was 27}
        $\dfrac{27}{75} = 0.36$ which is outside the action limits so take action.
        \end{step}

        \begin{step}{What action would be taken if the next sample was 15}
        $\dfrac{15}{75} = 0.2$ which is insied the warning limits so no action is taken.
        \end{step}

        \begin{step}{What action would be taken if the next sample was 3}
        $\dfrac{3}{75} = 0.04$ is bellow the warning limit so investigate how this low rate of non-conforming items may be maintained.
        \end{step}
